\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{color}
\usepackage[top=0.5in,bottom=0.75in,left=0.5in,right=0.5in,includehead,head=12pt,headsep=0.2in,includefoot,foot=12pt,footskip=0.25in]{geometry}
\usepackage{multicol}
\usepackage{array}
\usepackage{longtable}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{Microphones for The Perils of Pauline\hfill April 26, 2011}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{\hfil Page {\thepage} \hfil}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\title{Microphones for The Perils of Pauline}
\author{John Sauter}
\date{2011-04-26}
\begin{document}
\maketitle
\tableofcontents
\newpage

\section {Microphones}
In general, whenever an actor speaks, or sings by himself, he has a microphone.

\subsection {Assignments}
Microphones are assigned to actors as follows:

\begin{center}
\begin{longtable}{|l|m{7in}|}
\hline Mic. & Assignment \endhead \hline
\input perils.txt.assignments.tex
\end{longtable}
\end{center}

\subsection {Microphone Moves, by Page}

\begin{center}
\begin{longtable}{|l|m{7in}|}
\hline page & moves \endhead \hline
\input perils.txt.microphone_moves.tex
\end{longtable}
\end{center}

\subsection {Microphone Handling Instructions for Each Actor}

These instructions are formatted to be sliced into a strip of paper
for each of the actors to carry in order to remember his instructions.
In addition, the complete list can be posted near the shoe tree that
holds the microphones.

\vskip 0.25in

{\setlength{\parindent}{0in}
\input perils.txt.actors.tex
}

\subsection {List of Microphone Transactions for the Stage Manager}

\subsubsection {Initial Microphone Assignments}

These actors are the first to enter with their microphones:

\begin{center}
\begin{longtable}{|l|l|}
\hline Mic. & Actor \endhead \hline
\input perils.txt.stage_manager_before_show.tex
\end{longtable}
\end{center}

\subsubsection {Microphone Exchanges}

As the show progresses, some actors will have to share microphones. The
following list shows when microphones become free as actors leave the
stage, and when they go back into use on a different actor.

\begin{center}
\begin{longtable}{|l|l|l|l|}
\hline page & Mic. & Direction & Actor \endhead \hline
\input perils.txt.stage_manager_during_show.tex
\end{longtable}
\end{center}

\subsubsection {End of Show}

At the end of the show, retrieve the microphones from these actors

\begin{center}
\begin{longtable}{|l|l|}
\hline Mic. & Actor \endhead \hline
\input perils.txt.stage_manager_after_show.tex
\end{longtable}
\end{center}

\subsubsection {Intermission}

In case we start a rehearsal at the intermission, here are the microphone
assignments at the end of intermission.  This list can also be useful as a 
cross-check during a production.

\begin{center}
\begin{longtable}{|l|l|}
\hline Mic. & Actor \endhead \hline
\input perils.txt.stage_manager_at_intermission.tex
\end{longtable}
\end{center}

\subsubsection {Shoe Tree Labels}

When not being worn by an actor, the microphones are stored in a shoe tree,
which is 4 shoes wide by 6 shoes tall.  
Each slot has a space at the top 4.75 inches wide
by 1.5 inches high.  We provide here a label for each slot showing which
actors use that microphone, and when.

{\Large
\input perils.txt.microphone_labels.tex
}

\subsection {Front of House operator}

The Front of House operator controls the house mixer, 
which contains a volume slider
and mute button for each microphone.  

\subsubsection {Microphone Labels}

Associated with each slider is space to write a name.  
These spaces are 1 inch wide by 0.75 inch tall.  
Here is a label for each space:

{\Large
\input perils.txt.microphone_channels.tex
}

\subsubsection {Microphone Switching Instructions by Page}

These instructions are intended to be pasted into the script.

\input perils.txt.microphone_switching.tex

\end{document}
